\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-19 writing/draft1/draftMonika11.tex
draft writing
 bullet points what I will do in the future

\begin{itemize}
\item Cumulative precipitation and its square
\item Cumulative precipitation during the first two months of season
\item \textcolor{red}{I will also test cumulative precipitation  during the first month of each season - Guigma has promised to compute this variable}

\item Coefficient of variation
\item Maximum length of dry spell in number of days
\item Number of dry spell lasting for at least four days
\item Number of dry spell lasting for at least ten days
\item Number of dry spell lasting for at least twenty days
\item Maximum daily precipitation
\item \textcolor{red}{Additional indicators of floods - Guigma has promised to compute them over this weekend} 
\end{itemize}
\item \textbf{Temperature}
\begin{itemize}
\item Seasonal average (of daily average) and its square
\item Average maximum daily temperature
\item Standard deviation
\item Cumulative degree days $10-30\degree$C
\item Number of heatwave days $>35\degree$C
\end{itemize}
\end{itemize}
\subsection{Data}
\begin{itemize}
\item \textcolor{blue}{Source of data}
\item \textcolor{blue} {Verbal description of the data, resolution, period, frequency}
\item \textcolor{blue} {Plot(s)/barplots of yield, precip and temp when final data available}
\item \textcolor{blue}{Maybe a table of descriptive statistics or ref to the tale to appendix}
\item \textcolor{blue}{Description how the weather data were aggregated spatially over counties}

>>>>

\begin{itemize}
\item Cumulative precipitation and its square
\item Cumulative precipitation during the first two months of season
\item \textcolor{blue}{I will test cumulative precipitation  during the first month of each season - Guigma has has just provided the aggregated variables}

\item Coefficient of variation
\item Maximum length of dry spell in number of days
\item Number of dry spell lasting for at least four days
\item Number of dry spell lasting for at least ten days
\item Number of dry spell lasting for at least twenty days
\item Maximum daily precipitation
\color{blue}
\item Additional indicators of floods:

\begin{itemize}
\item One of the Climate Extreme Indices described at \url{https://www.climdex.org/indices.html} is the sum of precipitation amount on the days where precipitation is above 99th percentile of precip. of the whole period (i.e. 1981-2017 in our case). The 99th percentile is calculated based on the sample of wet days, that is the days where precipitation is above or equal to 1 mm (index no. 26)
\item Guigma has just sent me this measure and its varieties with thresholds 95th percentile and 90th percentile instead of the 99th percentile
\end{itemize}
\color{black}

\item \textbf{Temperature}
\begin{itemize}
\item Seasonal average (of daily average) and its square
\item Average maximum daily temperature
\item Standard deviation
\item Cumulative degree days $10-30\degree$C
\item Number of heatwave days $>35\degree$C
\end{itemize}
\end{itemize}

\subsection{Data}
\begin{itemize}
\item \textcolor{blue}{Source of data}
\item \textcolor{blue} {Verbal description of the data, resolution, period, frequency}
\item \textcolor{blue} {Plot(s)/barplots of yield, precip and temp when final data available}
\item \textcolor{blue}{Maybe a table of descriptive statistics or ref to the tale to appendix}
\item \textcolor{blue}{Description how the weather data were aggregated spatially over counties}
